Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
minor changes

For the majority of our benchmarks the conjecture explained
in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
solution in less than one minute.  This is possible if the inductive solutions need to be refined
with few counterexamples and fixed-point precision increases. However, two benchmarks in our set
required too many counterexamples to refine their solution (marked with $^*$ in Table~\ref{tab:results}). 
In these cases, the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.  This performance
difference is due to  the fact that the interval back-end does not take advantage of the inductive
conjecture inherent to CEGIS, but instead fully explores the counterexample space.  The result is
a performance difference of at least two orders of magnitude in our experiments, leading to the
interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
lists the faster of the two back-ends for each benchmark, which in 12 out of 14 cases is the inductive
back-end.

>>>>

For the majority of our benchmarks, the conjecture explained
in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
solution in less than one minute.  This is possible if the inductive solutions need to be refined
with few counterexamples and fixed-point precision increases. However, $2$ benchmarks in our set
required too many counterexamples to refine their solution (marked with $^*$ in Table~\ref{tab:results}). 
In these cases, the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.  This performance
difference is due to  the fact that the interval back-end does not take advantage of the inductive
conjecture inherent to CEGIS, but instead fully explores the counterexample space.  The result is
a performance difference of at least two orders of magnitude in our experiments, leading to the
interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
lists the faster of the two back-ends for each benchmark, which in $12$ out of $14$ cases is the inductive
back-end.
